Equivalence Testing and the Second Generation \emph{P}-Value

### 2018-08-28 manuscript.tex
pre-print submission

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV6-1.pdf}
\caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black
line) and SGPV (dotted grey line) across a range of observed sample
means (x-axis). Because the sample size is small (n = 10) and the CI is
more than twice as wide as the equivalence range (set to -0.4 to 0.4),
the SGPV is set to 0.5 (horizontal light grey line) across a range of
observed means.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TOSTSGPV6-1.pdf}
\caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black
line) and SGPV (dotted grey line) across a range of observed sample
means (x-axis). Because the sample size is small (n = 10) and the CI is
more than twice as wide as the equivalence range (set to -0.4 to 0.4),
the SGPV is set to 0.5 (horizontal lightgrey line) across a range of
observed means.}
\end{figure}
